\tool: Revisiting BadUSB with Type-C

### 2021-03-21 WOOT/Files/related_work.tex
JFA

\ac{MHL} extends the \ac{USB} standard and allows the video signal to
be transmitted through the \ac{USB} interface even for \ac{USB} 2.0 protocol. 
Juice Filming Attacks(JFA)~\cite{JFC},
abuses this standard and monitoring the victim's device utilizing \ac{USB} 2.0 protocol. Although the JFA~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
there are two main limitation compared with \tool: 
\ding{182} JFA~\cite{JFC} can only exfiltrate video data passively from the victim's device, while \tool can control the victim's device at the same time as monitoring the screen. All data can be collected by JFA only after the victim's interaction, while \tool can gather sensitive data actively through \ac{HID} injection. For example, if a victim leaves his/her phone charging without locking it, JFA cannot obtain anything in this case, while \tool can actively control his/her device and gather sensitive information.
\ding{183} The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest mobile devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of JFA. \tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}. So \tool has a wider attack range.

@@

In addition to injection attacks, data theft attack is also one of the focuses
of the academic community. As mentioned in Section~\ref{subsec:usb_attack}, there
exists an attack called JFA~\cite{JFC} which abuses the \ac{MHL}
standard to steal the video stream from the victim. In order to mitigate this
issue, Meng et al.~\cite{meng2018252} propose a statistical model using status
like GPU/CPU usage to detect JFA attacks.

>>>>

\ac{MHL} extends the \ac{USB} standard and allows the video signal to
be transmitted through the \ac{USB} interface even for \ac{USB} 2.0 protocol. 
\ac{JFA}~\cite{JFC},
abuses this standard and monitoring the victim's device utilizing \ac{USB} 2.0 protocol. Although \ac{JFA}~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
there are two main limitation compared with \tool: 
\ding{182} \ac{JFA}~\cite{JFC} can only exfiltrate video data passively from the victim's device, while \tool can control the victim's device at the same time as monitoring the screen. All data can be collected by \ac{JFA} only after the victim's interaction, while \tool can gather sensitive data actively through \ac{HID} injection. For example, if a victim leaves his/her phone charging without locking it, \ac{JFA} cannot obtain anything in this case, while \tool can actively control his/her device and gather sensitive information.
\ding{183} The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest mobile devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of \ac{JFA}. \tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}. So \tool has a wider attack range.

@@

In addition to injection attacks, data theft attack is also one of the focuses
of the academic community. As mentioned in Section~\ref{subsec:usb_attack}, there
exists an attack called \ac{JFA}~\cite{JFC} which abuses the \ac{MHL}
standard to steal the video stream from the victim. In order to mitigate this
issue, Meng et al.~\cite{meng2018252} propose a statistical model using status
like GPU/CPU usage to detect \ac{JFA} attacks.
